---
title: "Leaflet_week_41"
author: "Ida Bolther Holleufer"
date: "2023-10-12"
output: html_document
---
# Installing packages

```{r packages}
#install.packages("leaflet")
#install.packages("htmlwidgets")

library(leaflet)
library(htmlwidgets)
```

# Task 1. Create a Danish equivalent of AUSmap with esri layer but call it DANmap

### first do i have to create a location point
```{r location point}
popup2 = c("Copenhagen", "Odense", "Aarhus")
```

### Now that i have my lacation point, can i use leaflet to create a map.

```{r leaflet}
leaflet() %>%
  addTiles() %>%
  addProviderTiles("Esri.WorldImagery",
                   options = providerTileOptions(opacity=0.5)) %>%
  setView(lng = 10.21076, lat = 56.15674, zoom = 10)
                
```

### To create a map, do i have to do the steps below. 

```{r basemap}
l_dk <- leaflet() %>%   
  setView(10.21076, 56.15674, zoom = 13)
```

Now do i have to select backgrounds
```{r backgrounds}
esri <- grep("^Esri", providers, value = TRUE)
```

Selecting background
```{r selecting a background}
for (provider in esri) {
  l_dk<- l_dk %>% addProviderTiles(provider, group = provider)
}
```

Now can i create a map
```{r DANmap}
DANmap <- l_dk %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright")

DANmap
```
```{r libraries}
library(tidyverse)
library(googlesheets4)
library(leaflet)
```
Places in a google sheet
```{r places}
places <- read_sheet("https://docs.google.com/spreadsheets/d/1PlxsPElZML8LZKyXbqdAYeQCDIvDps2McZx1cTVWSzI/edit#gid=124710918",
                     range = "DigitalMethods",
                     col_types = "cccnncnc")

googlesheets4::gs4_deauth()
googlesheets4::gs4_auth()

glimpse(places)
```

# Task 2. Read in the googlesheet data you and your colleagues populated with data into the DANmap object you created in Task 1

```{r DANmap with markers}
DANmap %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = places$Description)
```


# Task 3: Can you cluster the points in Leaflet? Google "clustering options in Leaflet"
To be able to cluster the points shown in Leaflet, can i use the clusterOption. 

```{r cluster}
DANmap %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = places$Description, 
             clusterOptions = markerClusterOptions())
```

# Task 4: Look at the map and consider what it is good for and what not.
The map is good for a overview over the different citys location.
When zooming out, does the points cluster as we ask them to in task 3. This can make it hart to give a precise location, because to get that do we have to zoom in
When clustering the is map counting how many points there is. 
What the map doesn't show is ...

# Task 5: Find out how to display notes and classifications in the map.

In the previous task have i all ready createt notes, so that when i click on the points on the map, can i see what the point shows. 

If i want to add popups, a popup is a small box of information, containing arbitrary HTML, that will point to a specific point on the map, can i use the code

Danmark %>% 
addPopups([KOORDINATES]), [CONTENT],
options = popupOptions(closeButton = False)

The [] means that when you uses the code, do you have to change the information. 
So you have to use your own koordinates, and create your own content. 
To create a content, can i use the code

content <-paste(sep = "<br>",
  "<b><a> href='[link]'> [name of place]</a></b>",
  "[street and streat number]",
  "[city], [city code]")

